Insights Into Computational Reproducibility in Plant Pathology and a Way Forward

### 2020-12-07 analysis/paper/paper.Rmd
Fleshing out the discussion section

* Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with reproducible examples
for readers.

* Duku et al. [-@Duku2016] provide models, data and code, (http://adamhsparks.github.io/MICCORDEA/) necessary to
replicate the entire study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.

* Sparks et al. [-@Sparks2011; -@Sparks2014] provide models, data and code, (http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/)
necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.

* Lehner et al. [-@Lehner2017] provide data and a reproducible report that explains in detail all steps of the analysis and the R codes for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean tied (https://emdelponte.github.io/paper-white-mold-meta-analysis/).

* Khaliq et al. [] offer a full research compendium with a Docker instance and DOI that enable readers to fully replicate the analysis using the data collected and step through other points where weather data were investigated and various models were fit before deciding on the best fit.

* Example from Grünwald lab: 
  - paper http://apsjournals.apsnet.org/doi/full/10.1094/PHYTO-12-14-0350-FI
  - github repo https://github.com/grunwaldlab/Sudden_Oak_Death_in_Oregon_Forests
* Other examples from plant pathology providing e-Xtras or supplemental material

## A General Workflow

@@

To make your data the most widely usable, ensure that it has a persistent identifier.
A digital object identifier (DOI) is the most common (<https://www.doi.org/>) but handle is also an option (<https://handle.net/>).
There are different options for generating a DOI for your data and other materials.
FigShare, Zenodo and OSF all offer long-term archival along with a service to generate a DOI for your materials.
The use of a persistent identifier works to ensure that even if the data are moved, they can still be located using that unique identifier.

For more on FAIR data, visit Go-Fair <https://www.go-fair.org/fair-principles/>.

### Sharing Your Research

>>>>

Unfortunately using our scoring method, most articles scored poorly for reproducibility or openness.
Most journals in our discipline fail to mention the availability of the computational methods to support the article as published.

The software availability score was better as was the citing of software and versions used.
SAS remains firmly entrenched in the discipline as the choice of software for statistical analysis followed by SPSS.
It is interesting to note however, that with the popularity of Python that it does not even appear in our survey results whereas R was the fourth most commonly used software.

While the articles that were surveyed did not score well, we are aware of and would like to highlight that there are several good examples from the plant pathology discipline that can be used as exemplars.

There are different ways to make research more open and reproducible, which can be thought of as levels of reproducibility.
The first level is including tables of raw data or code with the paper as a supplemental file.
This is suitable for studies that may have a small data set or simple analysis or for demonstrations purposes as Madden et al. [-@Madden2015] demonstrate in their discussion regarding the use of $P$ values in statistical analyses where they supply an *e-**X**tra*\* with reproducible examples for readers to refer to.
This allows the reader to quickly view the extra materials and a DOI is assigned as a part of the article itself.

At the second level, Lehner et al. [-@Lehner2017] used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean tied (https://emdelponte.github.io/paper-white-mold-meta-analysis/).
The website clearly demonstrates the analysis for readers and uses R so that anyone can easily replicate the work.
Likewise, Duku et al. [-@Duku2016] provide scripts for models, data and code for graphs, via a website hosted by GitHub, http://adamhsparks.github.io/MICCORDEA/, that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.

The third level is the use of proper data repositories such as FigShare, Zenodo or OSF.io among others, allow for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation for a standalone citation. Sparks et al. [-@Sparks2011; -@Sparks2014] used FigShare to provide models, data and code, [@Sparks2016] necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.

The fourth level includes packaging the analysis as a software package, _e.g._ R Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq et al. [@Khaliq2020] have done. Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of chickpea ascochyta conida dispersal using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].

[@Miorini2018, @Miorini2019]

* Example from Grünwald lab: 
  - paper http://apsjournals.apsnet.org/doi/full/10.1094/PHYTO-12-14-0350-FI
  - github repo https://github.com/grunwaldlab/Sudden_Oak_Death_in_Oregon_Forests

## A general workflow

@@

To make your data the most widely usable, ensure that it has a persistent identifier.
A digital object identifier (DOI) is the most common (<https://www.doi.org/>) but handle is also an option (<https://handle.net/>).
There are different options for generating a DOI for your data and other materials.
FigShare, Zenodo and OSF all offer long-term archival along with a service to generate a DOI for your materials.
The use of a persistent identifier works to ensure that even if the data are moved, they can still be located using that unique identifier.
For more on FAIR data, visit Go-Fair <https://www.go-fair.org/fair-principles/>.

### Sharing your research
